\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-08 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\begin{IEEEkeywords}
Uncertainty propagation, power system dynamics, optimal transport, proximal operator.
\end{IEEEkeywords}

@@

The rest of this paper is structured as follows. Section \ref{sec:models} details the power system dynamics models at the microscopic or trajectory level (Sec. \ref{subsec:samplepathdynamics}) as well as at the macroscopic or statistical ensemble level (Sec. \ref{subsec:macroscopic}). The proposed idea of realizing the flow of the joint state PDFs subject to the macroscopic power system dynamics via infinite dimensional proximal recursions, is explained in Section \ref{sec:prox}. Section \ref{sec:ProxAlgo} elucidates the corresponding proximal algorithm that enables the computation of the transient joint state PDFs via weighted point cloud evolution. Numerical simulations are reported in Section \ref{sec:NumericalSimulations}. Section \ref{sec:conclusion} concludes the paper.

>>>>

\begin{IEEEkeywords}
Uncertainty propagation, power system dynamics, kinetic Fokker-Planck equation, proximal operator.
\end{IEEEkeywords}

@@

The rest of this paper is structured as follows. Section \ref{sec:models} details the power system dynamics models at the microscopic or trajectory level (Sec. \ref{subsec:samplepathdynamics}) as well as at the macroscopic or statistical ensemble level (Sec. \ref{subsec:macroscopic}). The proposed idea of realizing the flow of the joint state PDFs subject to the macroscopic power system dynamics via infinite dimensional proximal recursions, is explained in Section \ref{sec:prox}. Section \ref{sec:ProxAlgo} elucidates the corresponding proximal algorithm that enables the computation of the transient joint state PDFs via weighted point cloud evolution. Numerical simulations illustrating the proposed framework are reported in Section \ref{sec:NumericalSimulations}. Section \ref{sec:conclusion} concludes the paper.
